The KMOS Deep Survey (KDS): dynamical measurements of $z\sim3.5$ main sequence galaxies\thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: }

### 2017-04-03 paper.tex
ABOUT TO ADDRESS CHRIS COMMENTS APRIL 3rd

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[KDS I: dynamical properties of 77 z$\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: turner@roe.ac.uk (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements for 77 star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$ from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS).
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie on the red sequence, characterised by red optical colours, low star-formation rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star-formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main-sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, as regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high redshift main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}. 
To account for the growing number density of quiescent galaxies from z$\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e. quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item How applicable are strong-line metallicity calibrators at high redshift? \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes? 
\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}

This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work.
We seek also to minimise the impact of systematic differences introduced by the differing approaches in defining and extracting kinematic parameters when interpreting these trends.  
By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$. \\

The structure of the paper is as follows. In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
We present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The two key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the S/N required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate S/N across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest S/N and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
Predominantly, the galaxies were originally selected for spectroscopic follow-up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift.

@@

Two of the FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
In GOODS-S-P1 and GOODS-S-P2 we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies in GOODS-S-P2 does not include two targets which were later found to have $z < 0.5$.}

@@

We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical (SSA22-P2).
In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}. \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}

@@

Our data for the 77 KDS targets were observed using KMOS, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$).
\subsubsection{Observations}\label{subsubsec:Obs}

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of all 77 KDS galaxies in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density in of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that the KDS galaxies are all clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in Equation \protect\ref{eq:speagle_ms} as the green line, with the discrepancy between the two relations representating the expected main-sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\simeq3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

To achieve the science goals of the KDS the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, to facilitate both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
This paper is concerned with the spatially-resolved kinematics of the KDS galaxies, with the details of the {\it H}-band data reduction and corresponding metallicity analyses reserved for a future analysis.

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[KDS I: dynamical properties of 77 $z\simeq3.5$ galaxies]{The KMOS Deep Survey (KDS) I: dynamical measurements of typical star forming galaxies at $z\simeq3.5$ \thanks{Based on observations obtained at the Very Large Telescope of the European Southern Observatory. Programme IDs: 092.A-0399(A), 093.A-0122(A,B), 094.A-0214(A,B),095.A-0680(A,B),096.A-0315(A,B,C)}}

@@

\author[O.J. Turner et al.]{
O. J. Turner,$^{1,2,\thanks{E-mail: ojamesturner@icloud.com (OJT)}}$
M. Cirasuolo,$^{1,2}$
C. M. Harrison,$^{2,3}$
R. J. McLure,$^{1}$
J. S. Dunlop,$^{1}$\newauthor
A. M. Swinbank,$^{3,4}$
H. L. Johnson,$^{3,4}$
D. Sobral,$^{5}$
J. Matthee,$^{6}$
R. M. Sharples$^{3,4}$
\\
$^{1}SUPA\thanks{Scottish Universities Physics Alliance}$, Institute for Astronomy, University of Edinburgh, Royal Observatory, Edinburgh EH9 3HJ\\
$^{2}$European Southern Observatory, Karl-Schwarzschild-Str. 2, 85748 Garching b. M{\"u}nchen, Germany\\
$^{3}$Centre for Extragalactic Astronomy, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{4}$Institute for Computational Cosmology, Durham University, South Road, Durham, DH1 3LE, U.K.\\
$^{5}$Department of Physics, Lancaster University, Lancaster, LA1 4BY, U.K.\\
$^{6}$Leiden Observatory, Leiden University, PO Box 9513, NL-2300 RA Leiden, the Netherlands}

@@

% Abstract of the paper
\begin{abstract}
We present dynamical measurements from the KMOS ({\it K}-band Multi-Object Spectrograph) Deep Survey (KDS), which is comprised of 77 typical star-forming galaxies at $z\simeq3.5$ in the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$.
These measurements constrain the internal dynamics, the intrinsic velocity dispersions ($\sigma_{int}$) and rotation velocities ($V_{C}$) of galaxies in the high redshift Universe.
The mean velocity dispersion of the galaxies in our sample is $\sigma_{int} = 70.8^{+3.3}_{-3.1} kms^{-1}$, consistent with the increase of $\sigma_{int}$ with redshift reported up to $z\simeq3$ in other samples, to which we have made careful comparisons.
However only $34 \pm 8\%$ of our galaxies are rotation-dominated ($V_{C}/\sigma_{int}$ > 1), with the sample average $V_{C}/\sigma_{int}$ value much smaller than at lower redshift.
The rotation-dominated KDS galaxies show no clear offset from the local rotation velocity-stellar mass (i.e. $V_{C}-M_{\star}$) relation, although a smaller fraction of the galaxies are on the relation due to the increase in the dispersion-dominated fraction.
These observations are consistent with a simple equilibrium model picture, in which random motions are boosted in high redshift galaxies by the increase in gas fractions, accretion efficiency, specific star-formation rate and stellar feedback and may provide significant pressure support against gravity on the galactic disk scale.
\end{abstract}

@@

The galaxy population at all redshifts appears to be bimodal in many physical properties \citep[e.g. as described in][]{Dekel2006}, with a preference for the most massive galaxies to lie on the red sequence, characterised by red optical colours, low star-formation rates (SFRs) and spherical morphologies, and less massive galaxies in the blue sequence, characterised by blue colours, high star-formation rates and disky morphologies. 
For these blue, star-forming galaxies (SFGs) there is a roughly linear correlation between SFR and stellar mass ($M_{\star}$) \citep[e.g.][]{Daddi2007,Noeske2007,Elbaz2007}, in the sense that galaxies which have already accumulated a larger stellar population tend to have higher SFRs.
This correlation, or `main-sequence' underpins the `equilibrium model', in which the SFR of galaxies is regulated by the availability of gas, with outflows and accretion events sustaining the galaxy gas reservoirs in a rough equilibrium as the galaxy evolves \citep[e.g.][]{Dave2012,Lilly2013,Saintonge2013}.
The main-sequence has been studied comprehensively, using multi-wavelength SFR tracers, between $0 < z < 3$ \citep[e.g.][]{Rodighiero2011,Karim2011,Whitaker2012,Behroozi2013b,Whitaker2014,Rodighiero2014,Speagle2014,Pannella2014,Sobral2014,Sparre2015,Lee2015,Schreiber2015,Renzini2015,Nelson2016}, showing evolution of the relation towards higher SFRs at fixed $M_{\star}$ with increasing redshift, reflecting the increase of the cosmic Star-Formation Rate Density (SFRD) in this redshift range \citep{Madau_2014}.
At each redshift slice it has been suggested that galaxies on the main-sequence evolve secularly, regulated by their gas reservoirs, meaning that selecting such populations offers the chance to explore the evolution of the physical properties of typical SFGs across cosmic time.
This assumes that high redshift main-sequence galaxies are the progenitors of their lower redshift counterparts, which may not be the case \citep[e.g.][]{Gladders2013,Kelson2014,Abramson2016b} and also assumes that we can learn about galaxy evolution (i.e. how individual galaxies develop in physical properties over time) by studying the mean properties of populations at different epochs.

The picture is complicated by the addition of major and minor galaxy mergers which can rapidly change the physical properties of galaxies \citep[e.g.][]{Toomre1977,Lotz2008,Conselice2011,Conselice2014} and the relative importance of in-situ, secular stellar mass growth vs. stellar mass aggregation via mergers is the subject of much work involving both observations and simulations \citep[e.g.][]{Robaina2009,Kaviraj2012,Stott2013,Lofthouse2017,Qu2017}. 
To account for the growing number density of quiescent galaxies from $z\simeq2.5$ to the present day \citep[e.g.][]{Bell2004,Faber2007,Brown2007,Ilbert2010,Brammer2011,Muzzin2013,Buitrago2013} there must also be processes which shut off star-formation within main-sequence galaxies (i.e. quenching) which, to explain observations, must be a function of both mass and environment \citep{Peng2010,Darvish2016}.

@@

In this paper we present results from the KMOS Deep Survey (KDS), which is a guaranteed time programme focusing on the spatially-resolved properties of main-sequence SFGs at $z\simeq3.5$, a time when the universe was building to peak activity.
With this survey, we aim to complement existent studies by providing deep IFS data for the largest number of galaxies at this redshift.
By making use of KMOS (with integration times of 7.5-9 hours) we have been able to study [O~{\sc III}]$\lambda$5007 emission in 77 galaxies spanning the mass range $9.0 < log(M_{\star}/M_{\odot}) < 10.5$, roughly tripling the number of galaxies observed via IFS at $z > 3$.
In order to interpret the evolution of the physical properties of typical star-forming galaxies we have carefully constructed a set of comparison samples spanning $0 < z < 3$.
These samples use integral-field spectroscopy to track the ionised gas emission in star-forming galaxies and follow consistent kinematic parameter extraction methods.  
By doing this we seek to minimise the impact of systematic differences introduced by differing approaches to defining and extracting kinematic parameters.

There are still many open questions which we can begin to answer by studying the emission from regions of ionised gas within individual galaxies at these redshifts: \begin{enumerate}[label=(\roman*)] \item  What are the radial gradients in metal enrichment within these galaxies and what can this tell us about the physical mechanisms responsible for redistributing metals?
\item What are the dynamical properties of main-sequence galaxies at this early stage in their lifetimes? 
\item What is the connection between the gas-phase metallicity and  kinematics, particularly in terms of inflows and outflows of material? \end{enumerate}

This paper focuses on the third question by deriving and interpreting the spatially-resolved kinematics of the KDS galaxies, particularly the rotation velocities and velocity dispersions, using the [O~{\sc III}]$\lambda$5007 emission line, discussing what we can learn about the nature of galaxy formation at $z\simeq3.5$ and forming evolutionary links with lower redshift work. \\

The structure of the paper is as follows.
In \cref{sec:Survey_and_data} we present the survey description, sample selection, observation strategy and data reduction, leading to stacked datacubes for each of the KDS galaxies.
In \cref{sec:analysis} we describe the derivation of morphological and kinematic properties for our galaxies, explaining the kinematic modelling approach and the beam-smearing corrections which lead to intrinsic measurements of the rotation velocities, $V_{C}$, and velocity dispersions $\sigma_{int}$ for each of the galaxies classified as morphologically isolated and spatially-resolved in the [O~{\sc III}]$\lambda$5007 emission line.
\cref{sec:results} presents an analysis of these derived kinematic parameters, comparing with lower redshift work where possible and drawing conclusions about the evolutionary trends and possible underlying physical mechanisms.
We discuss these results in \cref{sec:discussion} and present our conclusions in \cref{sec:conclusion}.
Throughout this work we assume a flat $\Lambda$CDM cosmology with (h, $\Omega_{m}$, $\Omega_{\Lambda}$) = (0.7, 0.3, 0.7).

\section{SURVEY DESCRIPTION, SAMPLE SELECTION AND OBSERVATIONS}\label{sec:Survey_and_data}
\subsection{The KDS survey description and sample selection}\label{subsec:survey_intro}
The KDS is a KMOS study of the gas kinematics and metallicity in 77 SFGs with a median redshift of $z\simeq3.5$, probing a representative section of the galaxy main-sequence.
The addition of these data approximately triples the number of galaxies observed via IFS at this redshift \citep{Cresci2010,Lemoine-Busserolle2010,Gnerucci2011}, and will allow for a statistically-significant investigation of the dynamics and metal content of SFGs during a crucial period of galaxy evolution. 
The key science goals of the KDS are to investigate the resolved kinematic properties of high redshift galaxies in the peak epoch of galaxy formation ( particularly the fraction of rotating disks and the degree of disk turbulence) and also to study the spatial distribution of metals within these galaxies in the context of their observed dynamics.
We seek to probe both a `FIELD' environment in which the density of galaxies is typical for this redshift and a `CLUSTER' environment containing a known galaxy over-density, in order to gauge the role of environment in determining the kinematics and metallicities of SFGs during this early stage in their formation history.
To achieve this we require very deep exposure times in excess of 7 hours on source to reach the signal to noise required to detect line emission in the outskirts of the galaxies where the rotation curves begin to flatten, and to achieve adequate signal to noise across several ionised emission lines within individual spatial pixels (spaxels).
Consequently, the KDS is one of the deepest spectroscopic datasets available at this redshift.

\subsubsection{Sample selection}\label{subsubsec:sample_selection}
Target selection for the KDS sample is designed to pick out SFGs at $z\simeq3.5$, supported by deep, multi-wavelength ancillary data.
Within this redshift range the [O~{\sc III}]$\lambda$4959,$\lambda$5007 doublet and the $H\beta$ emission lines are visible in the {\it K}-band and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is visible in the {\it H}-band, both of which are observable with KMOS.
From these lines, [O~{\sc III}]$\lambda$5007 generally has the highest signal to noise and so is well suited to dynamical studies, whereas [O~{\sc III}]$\lambda$4959, $H\beta$ and the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet complement [O~{\sc III}]$\lambda$5007 as tracers of the galaxy metallicities. 
To ensure a high detection rate of the ionised gas emission lines in the KDS we select galaxies in well-studied fields that have a previous spectroscopic detection (see details below).
Predominantly, the galaxies were originally selected for spectroscopic follow-up using the Lyman-Break technique \citep{Steidel1996}, which is especially effective at picking out normal starforming galaxies at $z = 3-4$.
However, a subset of the selected cluster galaxies in the SSA22 field were blindly-detected in Ly$\alpha$ emission during a narrow-band imaging study of a known overdensity of Lyman Break Galaxies (LBGs) at $z\simeq3.09$ \citep{Steidel2000}.
We make no further cuts to the sample on the basis of mass and SFR, in order to probe a more representative region of the star-forming main-sequence at this redshift (see Figure \ref{fig:main_sequence}).

@@

Two of the three FIELD environment pointings are selected within the GOODS-S region \citep{Guo2013}; accessible from the VLT and with excellent multi-wavelength coverage, including deep {\em HST WFC3 F160W} imaging with a $0.06^{\prime\prime}$ pixel scale and $\simeq0.2^{\prime\prime}$ PSF, which is well suited for constraining galaxy morphology \citep{Grogin2011,Koekemoer2011}.
We selected targets from the various spectroscopic campaigns which have targetted GOODS-S, including measurements from VIMOS \citep{Balestra2010,Cassata2014}, FORS2 \citep{Vanzella2005,Vanzella2006,Vanzella2008} and both LRIS and FORS2 as outlined in \cite{Wuyts2009}.
These targets must be within the redshift range $3 < z < 3.8$, have high spectral quality (as quantified by the VIMOS redshift flag equal `3' or `4', and the FORS2 quality flag equal `A') and we carefully excluded those targets for which the [O~{\sc III}]$\lambda$5007 or H$\beta$ emission lines, observable in the {\it K}-band at these redshifts, would be shifted into a spectral region plagued by strong OH emission.
The galaxies which remain after imposing these criteria are distributed across the GOODS-S field, and we selected two regions where $\simeq20$ targets could be allocated to the KMOS IFUs (noting that the IFUs can patrol a $7.2^{\prime}$ diameter patch of sky during a single pointing).
We name these GOODS-S-P1 and GOODS-S-P2, which which we observe 20 and 17 galaxies respectively (see Table \ref{tab:pointings}).\footnote{We note that the number of observed galaxies quoted for GOODS-S-P2 does not include two observed targets which were later found to have $z < 0.5$.}

@@

We also added a further FIELD environment pointing to the south of the main SSA22 spatial overdensity where the density of galaxies is typical of the field environment (SSA22-P2).
In SSA22-P1 and SSA22-P2 we observe 19 and 21 galaxies respectively.
In summary we have chosen three FIELD environment pointings and a single CLUSTER environment pointing across GOODS-S and SSA22, comprising a total of 77 galaxies, as described in Table \ref{tab:pointings}. \footnote{Additional pointings in the COSMOS and UDS fields were originally scheduled as part of the GTO project, however 50$\%$ of the observing time was lost to bad weather during these visitor mode observations.}

@@

Our data for the 77 KDS targets were observed using KMOS \citep{Sharples2013}, which is a second generation IFS mounted at the Nasmyth focal plane on UT1 at the VLT.
The instrument has 24 moveable pickoff arms, each with an integrated IFU, which patrol a region 7.2$^{\prime}$ in diameter on the sky, providing considerable flexibility when selecting sources for a single pointing.
The light from each set of 8 IFUs is dispersed by a single spectrograph and recorded on a 2k$\times$2k Hawaii-2RG HgCdTe near-IR detector, so that the instrument is comprised of three effectively independent modules.
Each IFU has 14$\times$14 spatial pixels which are 0.2$^{\prime\prime}$ in size, and the central wavelength of the {\it K}-band grating has a spectral resolution of $R\simeq4200$ ({\it H}-band $R\simeq4000$).
\subsubsection{Observations}\label{subsubsec:Obs}

\begin{figure*}
    \centering \hspace{-1.3cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{rest_colour.png}
    \end{subfigure} \hspace{+0.4cm}
    \begin{subfigure}[h!]{0.5\textwidth}
        \centering
        \includegraphics[height=3.5in]{main_sequence.png}
    \end{subfigure}
    \caption{{\it Left:} The distribution of all 77 KDS galaxies in rest-frame UVJ colour space is plotted, with filled symbols showing galaxies detected in [O~{\sc III}]$\lambda$5007 and open symbols showing those which were not detected.
    Also plotted in this plane are $\simeq4000$ galaxies in GOODS-S with $3.0 < z < 3.8$ (mirroring the KDS redshift range) from the 3D-{\em HST} survey  \protect\citep{Brammer2012,Momcheva2016}, with the filled squares denoting the density of galaxies in that region.
    We use the galaxy selection criteria defined in \protect\cite{Whitaker2012a} to highlight star-forming and quiescent regions (motivated by the age sequence of quiescent galaxies), finding that all but one of the KDS galaxies are clearly in the star-forming region and overlap with the highest density of 3D-{\em HST} targets.
    {\it Right:} We plot the location of the KDS galaxies in the SFR versus M$_{\star}$ plane, using the same symbol convention. 
    The same GOODS-S galaxies from the 3D-{\em HST} survey as in the left panel are plotted with the filled squares as a reference for the typical relationship between SFR and $M_{\star}$.
    The black solid line and the dashed line show the $z\simeq2.5$ broken power-law and quadratic fit to the main-sequence respectively, described in \protect\cite{Whitaker2014}.
    We include the MS relation evaluated at $z=3.5$ (the median redshift of the KDS sample) described in \protect\cite{Speagle2014} and given in Equation \protect\ref{eq:speagle_ms} as the green line, with the discrepancy between the two relations representating the expected main-sequence evolution between these redshifts. 
    Within the typical uncertainties (see error bars) the KDS sample is representative of $z\simeq3.5$ SFGs.}
    \label{fig:main_sequence}
\end{figure*}

To achieve the science goals of the KDS, the target galaxies at $3 < z < 3.8$ were observed in both the {\it K}-band, into which the [O~{\sc III}]$\lambda$5007 and $H\beta$ lines are redshifted, and the {\it H}-band, into which the [O~{\sc II}]$\lambda$3727,$\lambda$3729 doublet is redshifted, facilitating both dynamical and chemical abundance measurements.
The GOODS-S pointings were observed in the {\it H} and {\it K}-bands separately, however due to loss of observing time the SSA22 galaxies were observed with the KMOS {\it HK} filter, which has the disadvantage of effectively halving the spectral resolution, but allows for coverage of the {\it H}-band and {\it K}-band regions simultaneously. \\

@@

This paper is concerned with the spatially-resolved kinematics of the KDS galaxies.
Consequently, we now focus exclusively on the spatially-resolved [O~{\sc III}]$\lambda$5007 measurements in the {\it K}-band spectral window. 
The details of the {\it H}-band data reduction and corresponding metallicity analyses will be described in a future study.
